

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% چکیده به‌صورتگلیسی

%در چكيده به‌صورتگليسي، می‌باید عينا" متن چكيده فارسي به زببه‌صورت به‌صورتگليسي ترجمه شود.
\section*{Abstract}
In various application domains, high-dimensional multi-label data has become more prevalent, presenting two significant challenges: instances with high-dimensional features and a large number of labels. In the context of multi-label feature selection, the objective is to choose a subset of features from a given set that is highly pertinent for predicting multiple labels or categories associated with each instance. However, certain characteristics of multi-label classification, such as label dependencies and imbalanced label distribution, have often been overlooked although hold valuable insights for designing effective multi-label feature selection algorithms. In this research, we propose a feature selection model which exploits explicit global and local label correlations to select discriminative features across multiple labels. In addition, by representing the feature matrix and label matrix in a shared latent space, the model aims to capture the underlying correlations between features and labels. The shared representation can reveal common patterns or relationships that exist across multiple labels and features. An objective function involving $\ell_{2,1} $-norm regularization is formulated, and an alternating optimization-based iterative algorithm is designed to obtain the sparse coefficients for multi-label feature selection. The proposed method was evaluated on twelve real-world multi-label datasets using six evaluation metrics, through comprehensive experiments. The results indicate its effectiveness, surpassing that of several representative methods.	\\
%کلمات کلیدی به‌صورتگلیسی نیز عينا" ترجمه‌ی کلمات کلیدی فارسی هستند.\\
\noindent\textbf{Keywords:}
{feature selection, multi-label learning, label correlation, nonnegative matrix factorization}


%%%%%%%%%%%
%%%%%%%%%%%%%%